Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-09-05 paper-correlations.tex
Replace bibliography file

\documentclass[reprint,amsmath,amssymb,aps,pre,nofootinbib]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\begin{document}
%*Corresponding author: Kirill M. Gerke, Tel.: +79661877715, E-mail: kg@ifz.ru,
%Address: Schmidt Institute of Physics of the Earth of Russian Academy of
%Sciences, Bolshaya Gruzinskaya str. 10/1, Moscow, 123242, Russia
\author{Vasily Postnicov}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 123242, Russia}
\author{Alexey I. Samarin}
\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow
  State University, Moscow, 119991, Russia}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 123242, Russia}
\author{Efim V. Lavrukhin}
\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow
  State University, Moscow, 119991, Russia}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 123242, Russia}
\author{Marina V. Karsanina}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 123242, Russia}
\author{Mathieu Gravey}
\altaffiliation{University of Lausanne, Faculty of Geosciences and Environment,
  Institute of Earth Surface Dynamics, Lausanne, Switzerland}
\author{Kirill M. Gerke}
\email[E-mail:]{kg@ifz.ru}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 123242, Russia}

@@

\section{Background and motivation}
Materials are ubiquitous both in nature and in industrial human activities, and
their physical properties are interconnected to
structure\cite{Torq_book}\cite{Sahimi_book}\cite{Adler_book}. The information
about the structure usually comes in the way of 2D and 3D images obtained by
microscopy, tomography and other related methodologies. This structural
information can be used for numerous types of analysis, including simulations of
different processes within studied materials or evaluation of their properties
using so-called pore-scale modelling. Unlike computational modelling techniques
a whole class of approximate methods exists including (rigorous) bounds that
allows very fast estimations of physical properties albeit the bounds themselves
are too wide to be applicable in majority of practical problems. Nonetheless, it
is noteworthy that such bounds are originally based on structural descriptors in
the form of correlation functions.

@@

There are different types of correlation functions that in general describe some
probabilities. The main parameter of any correlation function is the number of
points that are utilized to evaluate such a probability. While so-called
$n$-point probability function\cite{Torq_book} will totally describe any
structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
computing or storing such a function is not practical. Based on information
content, it was shown that increasing the number of point $n > 2$ only
marginally improves the quality of the structure quantification and these
improvements decay with increasing $n$. For stochastic reconstruction purposes
computation of higher-order statistics will, arguably, not be balanced by
increased number of points, but this is the topic of active research. For
aforementioned reasons, we mainly focus on 2-point statistics, leaving the
possibility to include higher order CFs in the future work. The simplest 2-point
probability function ($S_2$ or autocorrelation) actually arise from small angle
scattering experiments and measures the probability that both ends of line
segment with a given length fall into the same phase. Other types include the
probability of a whole line segment to fall into the phase ($L_2$ function) or
to lie on the interface between phases ($F_{ss}$ function), and mainly originate
from aforementioned bounds on physical properties such as permeability and
elasticity. The general idea of computation of different 2-point CFs is shown in
\cref{fig:functions}. All major details and numerous analytical cases can be
found in seminal work of Torquato \cite{Torq_book}. To all CFs described in this
book and applicable to digital images we shall refer as to classical correlation
functions.

@@

\onecolumngrid
\bibliography{habib}
\bibliographystyle{plain}
\twocolumngrid

\end{document}

>>>>

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs,nofootinbib]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\begin{document}
\preprint{APS/123-QED}

\author{Aleksei Samarin\textsuperscript{1,2}}
\author{Vasily Postnicov\textsuperscript{1}}
\author{Marina Karsanina\textsuperscript{1}}
\author{Efim Lavrukhin\textsuperscript{1,2}}
\author{Dina Gafurova\textsuperscript{3}}
\author{Aleksey Khlyupin\textsuperscript{1}}
\author{Kirill Gerke\textsuperscript{1}}
\email{kg@ifz.ru}

\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
  Russian Academy of Sciences, Moscow, 107031, Russia}
\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
  Lomonosov Moscow State University, Moscow, 119991, Russia}
\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}

@@

\section{Background and motivation}
Materials are ubiquitous both in nature and in industrial human activities, and
their physical properties are interconnected to
structure\cite{Torquato_book}\cite{Sahimi_book}\cite{Adler_recon}. The information
about the structure usually comes in the way of 2D and 3D images obtained by
microscopy, tomography and other related methodologies. This structural
information can be used for numerous types of analysis, including simulations of
different processes within studied materials or evaluation of their properties
using so-called pore-scale modelling. Unlike computational modelling techniques
a whole class of approximate methods exists including (rigorous) bounds that
allows very fast estimations of physical properties albeit the bounds themselves
are too wide to be applicable in majority of practical problems. Nonetheless, it
is noteworthy that such bounds are originally based on structural descriptors in
the form of correlation functions.

@@

There are different types of correlation functions that in general describe some
probabilities. The main parameter of any correlation function is the number of
points that are utilized to evaluate such a probability. While so-called
$n$-point probability function\cite{Torquato_book} will totally describe any
structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
computing or storing such a function is not practical. Based on information
content, it was shown that increasing the number of point $n > 2$ only
marginally improves the quality of the structure quantification and these
improvements decay with increasing $n$. For stochastic reconstruction purposes
computation of higher-order statistics will, arguably, not be balanced by
increased number of points, but this is the topic of active research. For
aforementioned reasons, we mainly focus on 2-point statistics, leaving the
possibility to include higher order CFs in the future work. The simplest 2-point
probability function ($S_2$ or autocorrelation) actually arise from small angle
scattering experiments and measures the probability that both ends of line
segment with a given length fall into the same phase. Other types include the
probability of a whole line segment to fall into the phase ($L_2$ function) or
to lie on the interface between phases ($F_{ss}$ function), and mainly originate
from aforementioned bounds on physical properties such as permeability and
elasticity. The general idea of computation of different 2-point CFs is shown in
\cref{fig:functions}. All major details and numerous analytical cases can be
found in seminal work of Torquato \cite{Torquato_book}. To all CFs described in this
book and applicable to digital images we shall refer as to classical correlation
functions.

@@

\bibliography{apssamp}
\end{document}
